%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    
    \cventry
    {Open Source} % Advisor
    {Digit Recognizer using dNNs} % Institution
    {Feb. 2022 - March 2022} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implimented Dense Neural Networks using TensorFlow and Keras in python to recognize digits.
        \\Accuracy: 99.5\%
    }
      \end{cvitems}
    }
    
    \cventry
    {SRM University, AP} % Advisor
    {SRM CloudNet} % Institution
    {Oct. 2022 - Present} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Lead the team that built SRM’s own private cloud network.
        \\Technology used: 20 high-performance Linux Servers, Openstack, BASH}
      \end{cvitems}
    }
    
    \cventry
    {SRM University, AP} % Advisor
    {ML Based Attendence System} % Institution
    {July 2021 - Sept. 2021} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Trained an ML Model to mark a person’s attendance if present.
        \\Accuracy: 88.6\%}
      \end{cvitems}
    }
    
    \cventry
    {Open Source} % Advisor
    {GBoard Material You} % Institution
    {May 2021 - Nov. 2021} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {An android recovery module written in BASH with 2.6k+ downloads, that enables MaterialYou in Android 12, and Other amazing tweaks in other Android versions.}
      \end{cvitems}
    }
    
    \cventry
    {Open Source} % Advisor
    {Environment \$PATH GUI} % Institution
    {June 2021 - July. 2021} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A tkinter based Python program, that gives users a GUI to add or remove environment paths (\$PATH)
        \\Support: MacOS, RedHat, Arch, Debian and their derivatives.
    }
      \end{cvitems}
    }

    
    \cventry
    {Open Source} % Advisor
    {Contributed to Archcraft and Pop\_OS!} % Institution
    {} % Location
    {} % Date(s)
    {      \begin{cvitems} % Description(s)
        \item {Contributed to Documentation in Pop\_OS! and Archcraft Linux.
    }
      \end{cvitems}}


%---------------------------------------------------------
\end{cventries}
